---
title: "QCSimulator.Rmd"
author: "Tinniam V Ganesh"
date: "June 22, 2016"
output: html_document
---

```{r }
library(QCSimulator)
library(ggplot2)
```

#Initialize the environment and set global variables
```{r}
rm(list=ls())
#Call the init function to initialize the environment and create global variables
init()

# Display global variables in environment
ls()
# 2 x 2 Identity matrix 
I2
# 8 x 8 Identity matrix 
I8
# Qubit |00>
q00_
# Qubit |010>
q010_
# Qubit |0100>
q0100_
# Qubit 10010
q10010_
```
### To display the unitary matrix of gates
To check the unitary matrix of gates we need to pass the appropriate
identity matrix. Hence below the qubit gates require a 2 x 2 unitary matrix
and the 2 & 3 qubit CNOT gates require a 4 x 4 and 8 x 8 identity matrix
respectivelt
```{r}

PauliX(I2)
Hadamard(I2)
S1Gate(I2)
CNOT2_10(I4)
CNOT3_20(I8)
```

### Applying gates
**Note** To apply a quantum gate the gate can be called by passing the identity matrix
to it. For e.g applying take a look at the following.

Q0 -- Hadamard - PauliZ
Q1 -- TGate- Hadamard
```{r}
Q0 = PauliZ(Hadamard(I2))
Q0
Q1 = Hadamard(TGate(I2))
Q1
```


### Compute the inner product of vectors
For example of phi = 1/2|0> + sqrt(3)/2|1> and si= 1/sqrt(2)(10> + |1>) then the 
inner product is the dot product of the vectors
```{r}
phi = matrix(c(1/2,sqrt(3)/2),nrow=2,ncol=1)
si = matrix(c(1/sqrt(2),1/sqrt(2)),nrow=2,ncol=1)
angle= innerProduct(phi,si)
cat("Angle between vectors is:",angle)
```


### Compute the dagger function for a gate
The gate dagger computes and displays the transpose of the complex conjugate of
the matrix
```{r}
TGate(I2)
GateDagger(TGate(I2))
```

### To display the unitary matrix of gates
To check the unitary matrix of gates we need to pass the appropriate
identity matrix. Hence below the qubit gates require a 2 x 2 unitary matrix
and the 2 & 3 qubit CNOT gates require a 4 x 4 and 8 x 8 identity matrix
respectivelt
```{r}

PauliX(I2)
Hadamard(I2)
S1Gate(I2)
CNOT2_10(I4)
CNOT3_20(I8)
```

#Invoking gates in series
The Quantum gates can be chained by passing each preceding Quantum gate as
the argument.

```{r}
# Call in reverse order
# Superposition states
# |+> state
Hadamard(q0_)
# |->
PauliZ(Hadamard(q0_))

# (+i) Y
 SGate(Hadamard(q0_))

# (-i)Y
 S1Gate(Hadamard(q0_))
```

### More gates in series
#### TGate of depth 2

The Quantum circuit for a TGate of Depth 2 is

Q0 ---   Hadamard-TGate-Hadamard-TGate-SGate-Measurement

```{r}
# Invoking this in reverse order we get

a = SGate(TGate(Hadamard(TGate(Hadamard(q0_)))))
result=measurement(a)

plotMeasurement(result)

```




### Invoking gates in parallel
To obtain the results of gates in parallel we have to taje the Tensor Product

Q0  -- Hadamard-Measurement
Q1  -- Identity- Measurement
```{r}
# 
a = TensorProd(Hadamard(I2),I2)
b = DotProduct(a,q00_)
plotMeasurement(measurement(b))

a = TensorProd(PauliZ(I2),Hadamard(I2))
b = DotProduct(a,q00_)
plotMeasurement(measurement(b))

```


# Measurement
The measurement of a Quantum circuit can be obtained using the meaurement function.
Consider the following Quantum circuit

Q0 - H-T-H-T-S-H-T-H-T-H-T-H-S-Measurement
where H - Hadamard gate, T - T Gate and S- S Gate
```{r}
a = SGate(Hadamard(TGate(Hadamard(TGate(Hadamard(TGate(Hadamard(SGate(TGate(Hadamard(TGate(Hadamard(I2)))))))))))))
measurement(a)
```


### Plot measurement
Using the same example as above 
Q0 - H-T-H-T-S-H-T-H-T-H-T-H-S-Measurement
where H - Hadamard gate, T - T Gate and S- S Gate 
we can plot the measurement
```{r}
a = SGate(Hadamard(TGate(Hadamard(TGate(Hadamard(TGate(Hadamard(SGate(TGate(Hadamard(TGate(Hadamard(I2)))))))))))))
result = measurement(a)
plotMeasurement(result)
```


### Evaluating a Quantum Circuit 
The above procedure for evaluating a quantum gates in series and parallel can be 
used to evalute more complex quantum circuits were the quantum gates are in series
and parallel.

Here is an evaluation of one such circuit, the Bell ZQ state using the QCSimulator
```{r}
# 1st composite
a = TensorProd(Hadamard(I2),I2)
# Output of CNOT
b = CNOT2_01(a)
# 2nd series
c=Hadamard(TGate(Hadamard(SGate(I2))))
#2nd composite
d= TensorProd(I2,c)
# Output of 2nd composite
e = DotProduct(b,d)
#Action of quantum circuit on |00>
f = DotProduct(e,q00_)
result= measurement(f)
plotMeasurement(result)
```

###Toffoli State
This circuit for this comes from IBM's Quantum Experience. This circuit
is available in the package. This is how the state was constructed
```{r}
  # Computation of the Toffoli State
    H=1/sqrt(2) * matrix(c(1,1,1,-1),nrow=2,ncol=2)
    I=matrix(c(1,0,0,1),nrow=2,ncol=2)

    # 1st composite
    # H x H x H
    a = TensorProd(TensorProd(H,H),H)
    # 1st CNOT
    a1= CNOT3_12(a)

    # 2nd composite
    # I x I x T1Gate
    b = TensorProd(TensorProd(I,I),T1Gate(I))
    b1 = DotProduct(b,a1)
    c = CNOT3_02(b1)

    # 3rd composite
    # I x I x TGate
    d = TensorProd(TensorProd(I,I),TGate(I))
    d1 = DotProduct(d,c)
    e = CNOT3_12(d1)

    # 4th composite
    # I x I x T1Gate
    f = TensorProd(TensorProd(I,I),T1Gate(I))
    f1 = DotProduct(f,e)
    g = CNOT3_02(f1)

    #5th composite
    # I x T x T
    h = TensorProd(TensorProd(I,TGate(I)),TGate(I))
    h1 = DotProduct(h,g)
    i = CNOT3_12(h1)

    #6th composite
    # I x H x H
    j = TensorProd(TensorProd(I,Hadamard(I)),Hadamard(I))
    j1 = DotProduct(j,i)
    k = CNOT3_12(j1)

    # 7th composite
    # I x H x H
    l = TensorProd(TensorProd(I,Hadamard(I)),Hadamard(I))
    l1 = DotProduct(l,k)
    m = CNOT3_12(l1)
    n = CNOT3_02(m)

    #8th composite
    # T x H x T1
    o = TensorProd(TensorProd(TGate(I),Hadamard(I)),T1Gate(I))
    o1 = DotProduct(o,n)
    p = CNOT3_02(o1)
    result = measurement(p)
    plotMeasurement(result)
```

### GHZ YYX measurement
```{r}
a = TensorProd(TensorProd(Hadamard(I2),Hadamard(I2)),PauliX(I2))
b= CNOT3_12(a)
c= CNOT3_02(b)
d= TensorProd(TensorProd(Hadamard(I2),Hadamard(I2)),Hadamard(I2))
e= DotProduct(d,c)
f= TensorProd(TensorProd(S1Gate(I2),S1Gate(I2)),Hadamard(I2))
g= DotProduct(f,e)
i= TensorProd(TensorProd(Hadamard(I2),Hadamard(I2)),I2)
j = DotProduct(i,g)
result=measurement(j)
plotMeasurement(result)
```

