---
title: "QCSimulator.Rmd"
author: "Tinniam V Ganesh"
date: "June 22, 2016"
output: html_document
---

```{r }
library(QCSimulator)
library(ggplot2)
```

#Initialize the environment and set global variables
```{r}
rm(list=ls())
#Call the init function to initialize the environment and create global variables
init()

# Display global variables in environment
ls()
# 2 x 2 Identity matrix 
I2
# 8 x 8 Identity matrix 
I8
# Qubit |00>
q00_
# Qubit |010>
q010_
# Qubit |0100>
q0100_
# Qubit 10010
q10010_
```

### Compute the inner product of vectors


### Compute the dagger function for a gate
### To check the unitary matrix of gates
To check the unitary matrix of gates we need to pass the appropriate
identity matrix. Hence below the qubit gates require a 2 x 2 unitary matrix
and the 2 & 3 qubit CNOT gates require a 4 x 4 and 8 x 8 identity matrix
respectivelt
```{r}

PauliX(I2)
Hadamard(I2)
S1Gate(I2)
CNOT2_10(I4)
CNOT3_20(I8)
```

#Invoking gates in series

```{r}
# Call in reverse order
# Superposition states
# |+> state
Hadamard(q0_)
# |->
PauliZ(Hadamard(q0_))

# (+i) Y
 SGate(Hadamard(q0_))

# (-i)Y
 S1Gate(Hadamard(q0_))
```

### More gates in series
#### TGate of depth 2

The Quantum circuit for a TGate of Depth 2 is

Q0 ---   Hadamard-TGate-Hadamard-TGate-SGate-Measurement

```{r}
# Invoking this in reverse order we get

a = SGate(TGate(Hadamard(TGate(Hadamard(q0_)))))
result=measurement(a)

plotMeasurement(result)

```




### Invoking gates in parallel
To obtain the results of gates in parallel we have to taje the Tensor Product


```{r}
# Creating the Entangled state
a = TensorProd(Hadamard(I2),I2)
b = DotProduct(a,q00_)
```


# Measurement


### Plot measurement
